---
title: "Mathematical Examples with LaTeX"
author: "Your Name"
format:
  pdf:
    papersize: a4
    fontsize: 11pt
    sansfont: "GillSans"
    seriffont: "Bembo Std"
---

```{r}
#| include: false
source("_extensions/maxima/knitr-engine.R")

# Helper function for inline Maxima
maxima_inline <- function(code) {
  code <- sub(";\\s*$", "", code)
  cmd <- sprintf("maxima --very-quiet --batch-string='tex(%s);'", code)
  result <- system(cmd, intern = TRUE)
  latex <- grep("^\\$\\$", result, value = TRUE)
  if (length(latex) > 0) {
    return(gsub("\\$\\$", "", latex))
  }
  return("")
}
```

# Introduction

This document demonstrates using Quarto with LaTeX for mathematical typesetting.

# Calculus Examples

## Derivatives

The derivative of a function $f(x)$ is defined as:

$$
f'(x) = \lim_{h \to 0} \frac{f(x+h) - f(x)}{h}
$$

Some common derivatives:

- $\frac{d}{dx}(x^n) = n x^{n-1}$
- $\frac{d}{dx}(e^x) = e^x$
- $\frac{d}{dx}(\sin x) = \cos x$

## Integration

The fundamental theorem of calculus states:

$$
\int_a^b f(x) \, dx = F(b) - F(a)
$$

where $F'(x) = f(x)$.

# Linear Algebra

A system of linear equations can be written in matrix form:

$$
\mathbf{A}\mathbf{x} = \mathbf{b}
$$

For example:

$$
\begin{pmatrix}
2 & 1 & -1 \\
-3 & -1 & 2 \\
-2 & 1 & 2
\end{pmatrix}
\begin{pmatrix}
x_1 \\ x_2 \\ x_3
\end{pmatrix}
=
\begin{pmatrix}
8 \\ -11 \\ -3
\end{pmatrix}
$$

# Complex Analysis

Euler's formula is one of the most beautiful equations in mathematics:

$$
e^{i\theta} = \cos\theta + i\sin\theta
$$

When $\theta = \pi$, we get Euler's identity:

$$
e^{i\pi} + 1 = 0
$$

# Series and Sequences

The Taylor series expansion of $e^x$ around $x=0$ is:

$$
e^x = \sum_{n=0}^{\infty} \frac{x^n}{n!} = 1 + x + \frac{x^2}{2!} + \frac{x^3}{3!} + \cdots
$$

# Conclusion

This demonstrates Quarto's integration with LaTeX for beautiful mathematical typesetting.

## Maxima Examples

Using Maxima for symbolic computation: $\int x^2 \, dx = `r maxima_inline("integrate(x^2, x)")`$

Another example: The derivative of $\sin(x)\cos(x)$ is $`r maxima_inline("diff(sin(x)*cos(x), x)")`$.

Solving equations:

```{maxima}
#| tex: true
#| output: asis
#| echo: false
solve([x+y=5, x-y=1], [x,y]);
```

Differentiation:

```{maxima}
#| tex: true
#| output: asis
#| echo: false
diff(sin(x)*cos(x), x);
```

Expanding a polynomial:

```{maxima}
#| tex: true
#| output: asis
#| echo: false
expand((x+y)^3);
```

```{r, echo=FALSE}
print(letters)
```

```{python}
print("Hello World!")
```

